SMT-Boosted Security Types and Correctness for Low-Level MPC

### 2025-11-24 toplas26/examples.tex
checkpoint

In Section \ref{section-smt} we gave the example of 3-party additive
sharing for any field $\fieldp{p}$, in Section \ref{section-sty} we
discussed the example of YGC input encoding, and in Sections
\ref{section-metalang} and \ref{section-metaty} we presented and
discussed the example of gates in the GMW protocol for binary
circuits. In this section we present an extended example of 2-party
arithmetic circuits with multiplication gates defined using Beaver triples
\cite{evans2018pragmatic}. We first define a compositional gate
library in $\metaprot$ with correctness conditions defined using the
Hoare logic developed in Section \ref{section-metalang}, along with a
small example circuit.  Then we will extend the library with type
annotations illustrating the use of share types developed in
Sections \ref{section-sty} and \ref{section-metaty} to enforce
confidentiality properties. Last, we will extend the base library
with additional pre and postcondition annotations to enforce
integrity properties supported by BDOZ/SPDZ style MACs
\cite{SPDZ1,SPDZ2,BDOZ,10.1007/978-3-030-68869-1_3}.

\paragraph{Implementation and Evaluation}
We have implemented the $\metaprot$ language and automated Hoare logic
using an Antlr parser and Scala backend with cvc5 Java bindings for
interaction with the Satisfiability Modulo Fields theory.  To evaluate
performance, we have written and verified gate libraries and small
circuits using the GMW protocol for binary circuits as excerpted in
Figure \ref{fig-gmwprepost} in Section \ref{section-metalang}, and for
passive and malicious secure arithmetic circuits using Beaver Triple
multiplication as presented in Figures \ref{fig-beaver} and
\ref{fig-beaver-bdoz} in this Section.  We have considered field sizes
typically used to encode binary, 16 bit, 32 bit, and 64 bit
integers. Results are presented in Figure \ref{fig-preludetest}. In
summary, verification is efficient, largely due to the performance of
underlying cvc5 verification. It is categorically better performance
than can be achieved using previous brute-force methods developed in
$\fieldp{2}$ \cite{skalka-near-ppdp24}.

@@

A \ttt{sum} gate can be defined non-interactively using the
homomorphic addition. The correctness \ttt{postcondition} is simple
and perhaps unecessary to accelerate circuit verification, but is
appealing declaratively.  The multiplication gate \ttt{mult} is more
complex. We use the common approach of \emph{Beaver Triples}
\cite{evans2018pragmatic}. Recall that Beaver triples are values
$a,b,c$ with $a$ and $b$ chosen randomly and $c = a * b$, unique per
multiplication gate, that are secret-shared with clients during a
pre-processing phase by an assumed oracular client $\ttt{3}$.
The uniqueness requirement is necessary because
$a$ and $b$ are random values that serve as OTP masks for secure
openings, implemented as \ttt{secopen}. In our encoding we follow the
convention that each gate output identifier distinguishes the Beaver
triple, so for example the share of the $a$ value for a gate
$\ttt{"g"}$ is identified by $\ttt{"ga"}$, etc. The correctness
property of the multiplication gate, expressed as a
\ttt{postcondition}, relies on the $\ttt{BEAVERTRIP}$
precondition. This compositional correctness property can then be used
in circuit construction, without the need for ``re-proof'' in our
Hoare logic inference.

The circuit itself is constructed in \ttt{main} using these
gates. This is a small example but arbitrarily large circuits
can be constructed with this library. The precondition of
\ttt{main} must require distinct Beaver triples for each
multiplication gate in the circuit. The postcondition allows
verification of circuit correctness-- that the protocol
output is equal to the ideal functionality $\ttt{IDEALF}$.

>>>>

In Section \ref{section-smt} we gave the example of 3-party additive
sharing for any field $\fieldp{p}$, in Section \ref{section-sty} we
discussed the example of YGC input encoding, and in Sections
\ref{section-metalang} and \ref{section-metaty} we presented and
discussed the example of gates in the GMW protocol for binary
circuits. In this section we present an extended example of 2-party
arithmetic circuits with multiplication gates defined using Beaver
triples \cite{evans2018pragmatic}. We first define a compositional
gate library in $\metaprot$ with correctness conditions defined using
the Hoare logic developed in Section \ref{section-metalang}, along
with a small example circuit (Figure \ref{fig-beaver}).  Then we
extend the library with type annotations illustrating the use of share
types developed in Sections \ref{section-sty} and \ref{section-metaty}
to enforce confidentiality properties (Figure
\ref{fig-beaver-types}). Lastly, we extend the base library with
additional pre and postcondition annotations to enforce integrity
properties supported by BDOZ/SPDZ style MACs
\cite{SPDZ1,SPDZ2,BDOZ,10.1007/978-3-030-68869-1_3} (Figure
\ref{fig-beaver-bdoz}).

\paragraph{Implementation and Evaluation}
We have implemented the $\metaprot$ language and automated Hoare logic
using an Antlr parser and Scala backend with cvc5 Java bindings for
interaction with the Satisfiability Modulo Fields theory.  To evaluate
performance, we have written and verified gate libraries and small
circuits using the GMW protocol for binary circuits as excerpted in
Figure \ref{fig-gmwprepost} in Section \ref{section-metalang}, and for
passive and malicious secure arithmetic circuits using Beaver Triple
multiplication as presented in Figures \ref{fig-beaver} and
\ref{fig-beaver-bdoz} in this Section.  We have considered field sizes
typically used to encode binary, 16 bit, 32 bit, and 64 bit
integers. Results are presented in Figure \ref{fig-preludetest}. In
summary, verification is efficient, largely due to the performance of
underlying cvc5 verification, with categorically better performance
than can be achieved using previous brute-force methods developed in
$\fieldp{2}$ \cite{skalka-near-ppdp24}.

@@

A \ttt{sum} gate can be defined non-interactively using 
homomorphic addition. The correctness \ttt{postcondition} is simple
and perhaps unecessary to accelerate circuit verification, but is
appealing declaratively.  The multiplication gate \ttt{mult} is more
complex, where we use the common approach of \emph{Beaver Triples}
\cite{evans2018pragmatic}. Recall that Beaver triples are values
$a,b,c$ with $a$ and $b$ chosen randomly and $c = a * b$, unique per
multiplication gate, that are secret-shared with clients during a
pre-processing phase by an assumed oracular client $\ttt{3}$.
The uniqueness requirement is necessary because
$a$ and $b$ are random values that serve as OTP masks for secure
openings, implemented as \ttt{secopen}. In our encoding we follow the
convention that each gate output identifier distinguishes the Beaver
triple, so for example the share of the $a$ value for a gate
$\ttt{"g"}$ is identified by $\ttt{"ga"}$, etc. The correctness
property of the multiplication gate, expressed as a
\ttt{postcondition}, relies on the $\ttt{BEAVERTRIP}$
precondition. This compositional correctness property can then be used
in circuit construction, without the need for ``re-proof'' in our
Hoare logic inference.

The circuit itself is constructed in \ttt{main} using these
gates. This is a small example but arbitrarily large circuits can be
constructed with this library. The precondition of \ttt{main} requires
distinct Beaver triples for each multiplication gate in the circuit
(just one in this example). The postcondition allows verification of
circuit correctness-- that the protocol output is equal to the ideal
functionality $\ttt{IDEALF}$.
